Output Summary

### 2023-09-11 03-post-process/ms-content/ms-content.Rmd
ms-content: update color aesthetics

    # draw axis
    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
    par(mgp = nmgp)
    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
    axis(side = 2, at = (mp1 + mp2)/2, labels = tick_labels, las = 1)
    par(mpg = omgp)
  }

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
solid_col = "grey30"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3

@@

  # add posterior mean predicted curve
  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)

@@

  # add posterior mean predicted curve
  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col)

@@

  # add posterior mean predicted curve
  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col, lwd = 2)

@@

  # add posterior mean predicted curve
  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2, lty = lty[i])

@@

  # add posterior mean of predicted curve
  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col, lwd = 2)

@@

  # add posterior mean of predicted curve
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col, lwd = 2)

@@

# draw the posterior mean regression line
lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col)

# draw the population-specific capacity estimates w/error bars and labels
segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col)
segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col, lwd = 3)
points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col, bg = solid_col)

@@

junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 7, col = "white")
segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "white", lwd = 2)
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "white", lwd = 4)
segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 6, col = "black")
segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "black")
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "black", lwd = 3)

>>>>

    # draw axis
    omgp = par("mgp"); nmgp = omgp; nmgp[2] = 0.15
    par(mgp = nmgp)
    usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
    segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))
    axis(side = 2, at = (mp1 + mp2)/2, labels = tick_labels, las = 1)
    par(mgp = omgp)
  }

@@

```{r relationship-fig, fig.width = 7.2, fig.height = 9, fig.cap = msdown::prep_caption(relationship_caption), time_it = TRUE, eval = params$relationship_fig}
solid_col = "grey30"
solid_col2 = "black"
tranp_col = alpha(solid_col, 0.25)
pt_cex = 1.3

@@

  # add posterior mean predicted curve
  lines(phi_E_Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col2)

@@

  # add posterior mean predicted curve
  lines(Pb_pred["mean",] ~ E_pred, lwd = 2, col = solid_col2)

@@

  # add posterior mean predicted curve
  lines(pred_L_Pb_mean ~ E_scaled_seq, col = solid_col2, lwd = 2)

@@

  # add posterior mean predicted curve
  lines(pred_phi_Pa_Mb_mean ~ L_Pb_seq, col = solid_col2, lwd = 2, lty = lty[i])

@@

  # add posterior mean of predicted curve
  lines(pred_L_Mb_mean ~ L_Pb_seq, col = solid_col2, lwd = 2)

@@

  # add posterior mean of predicted curve
  lines(pred_phi_Mb_Ma_mean ~ L_Mb_seq, col = solid_col2, lwd = 2)

@@

# draw the posterior mean regression line
lines(pred_beta_summ["mean",] ~ wul_seq, lwd = 2, lty = 2, col = solid_col2)

# draw the population-specific capacity estimates w/error bars and labels
segments(jags_data$wul, beta_ests["2.5%",], jags_data$wul, beta_ests["97.5%",], col = solid_col2)
segments(jags_data$wul, beta_ests["10%",], jags_data$wul, beta_ests["90%",], col = solid_col2, lwd = 3)
points(beta_ests["mean",] ~ jags_data$wul, cex = 1.5, pch = 21, col = solid_col2, bg = solid_col2)

@@

junk = sapply(1:nrow(mp), function(i) pop_rhos(rownames(rho_mean_out)[i], mp[i,]))
segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 5, col = "white")
segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "white", lwd = 2)
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "white", lwd = 3)

segments(rho_mean_out[,"25%"], mp, rho_mean_out[,"75%"], mp, lwd = 4, col = "black")
segments(rho_mean_out[,"2.5%"], mp, rho_mean_out[,"97.5%"], mp, col = "black", lwd = 1)
points(mp ~ rho_mean_out[,"mean"], pch = 3, cex = 1, col = "black", lwd = 2)
